\input{../../../../msc/tex/HWSetup}

%
% Homework Details
%   - Title
%   - Subtitle
%   - Due date
%   - Due time
%   - Course
%   - Section/Time
%   - Instructor
%   - Author
%

\newcommand{\hmwkTitle}{Homework 03}
\newcommand{\hmwkSubTitle}{Ground Tracks}
\newcommand{\hmwkDueDate}{March 13, 2025}
\newcommand{\hmwkDueTime}{09:30 AM}
\newcommand{\hmwkClass}{ENAE 404 - 0101}
\newcommand{\hmwkClassTime}{09:30}
\newcommand{\hmwkClassInstructor}{Dr. Barbee}
\newcommand{\hmwkAuthorName}{\textbf{Vai Srivastava}}
\newcommand{\hmwkCompletionDate}{\today}

\begin{document}

\maketitle

\pagebreak

\begin{hwkProblem}{1}{}

	Conceptual questions:
	\begin{enumerate}
		\item Give the semi-major axis, eccentricity and inclination of an orbit whose ground track is a point.
		\item Explain why argment of periapsis equal to \qty{0}{\degree} or \qty{180}{\degree} produces equatorial symmetry.
		\item Consider the Molniya orbit. Which one orbital element would you change so that the spacecraft would spend a long time veiewing the Southern hemisphere (rather than the Northern hemisphere)? Identify the orbital element and the value of this orbital element that would preserve the same structure of the ground track (just flipped to observe the Southern hemisphere).
	\end{enumerate}

	\hwkSol

\end{hwkProblem}
\begin{hwkProblem}{2}{}

	Plot one day ground tracks for the following orbits:
	\begin{center}
		\begin{tabular}{cccccc}
			\hline Spacecraft ID & \( \mathrm{a}(\unit{\km}) \) & e   & \( \mathrm{i}(\unit{\degree}) \) & \( \Omega(\unit{\degree}) \) & \( \omega(\unit{\degree}) \) \\
			\hline
			A                    & 42164                        & 0.3 & 40                               & 0                            & 0                            \\
			B                    & 26562                        & 0.3 & 40                               & 0                            & 0                            \\
			C                    & 42164                        & 0.3 & 60                               & 0                            & 70                           \\
			D                    & 42164                        & 0.3 & 30                               & 0                            & 70                           \\
			E                    & 42164                        & 0.3 & 120                              & 0                            & 0                            \\
			\hline
		\end{tabular}
	\end{center}
	Compare and contrast the ground track for Orbit E to that of Orbit A.

	\hwkSol

\end{hwkProblem}
\begin{hwkProblem}{3}{}

	Calculate the \( \Delta \mathrm{V} \) required to execute a Hohmann transfer from a circular orbit with radius \qty{14e3}{\km} to a circular orbit with radius \qty{8e3}{\km}. Assume the central body is the Earth. State whether the maneuvers increase or decrease the spacecraft's velocity.

	\hwkSol

\end{hwkProblem}
\end{document}
