\input{/Users/vsrivastava/files/uni/msc/tex/HWSetup}

%
% Homework Details
%   - Title
%   - Due date
%   - Class
%   - Section/Time
%   - Instructor
%   - Author
%

\newcommand{\hmwkTitle}{Week 11 Discussion}
\newcommand{\hmwkDueDate}{November 11, 2024}
\newcommand{\hmwkDueTime}{11:59 PM}
\newcommand{\hmwkClass}{HISP 200}
\newcommand{\hmwkClassTime}{Section 0101}
\newcommand{\hmwkClassInstructor}{Prof. Woehlke}
\newcommand{\hmwkAuthorName}{\textbf{Vai Srivastava}}
\newcommand{\hmwkCompletionDate}{\today}

\begin{document}

\maketitle

\pagebreak

\begin{hwkProblem}{1}{}*
	What is the original name of UMD?

	\hwkSol

	The original name of UMD is "the Maryland Agricultural College".
\end{hwkProblem}

\begin{hwkProblem}{2}{}*
	What year was the University of Maryland Established with this original name? 

	\hwkSol

	The University of Maryland was established with this original name in 1856.
\end{hwkProblem}

\begin{hwkProblem}{3}{}*
	Who is the benefactor that contributed the land to establish the university?

	\hwkSol

	The benefactor that contributed the land to establish the university was Charles Benedict Calvert.
\end{hwkProblem}

\begin{hwkProblem}{4}{}*
	What is the name of the person that sued the University of Maryland to become the first Black graduate student to attend all of their classes on Campus?

	\hwkSol

	The person that sued the University of Maryland to become the first Black graduate student to attend all of their classes on Campus was Parren J. Mitchell.
\end{hwkProblem}

\begin{hwkProblem}{5}{}*
	Who is the artist and emeritus professor that had an arts center focused on African Diaspora studies named after them?

	\hwkSol

	The artist and emeritus professor that had an art center focused on African Diaspora studies named after them is David C. Driskell.
\end{hwkProblem}

\begin{hwkProblem}{6}{}*
	Who was the first African-American Director of the National Science Foundation, and what was their connection to the University of Maryland?

	\hwkSol

	The first African-American Director of the National Science Foundation was Chancellor John B. Slaughter, who was the first African-American leader on UMD's campus, and who made advances in the recruitment and retention of African-Anerican students and faculty at UMD.
\end{hwkProblem}

\begin{hwkProblem}{7}{}*
	What is the name of the African American lawyer denied enrollment to the University of Maryland Law School, but went on to become the first African American Supreme Court Justice of the United States?

	\hwkSol

	The African-American lawyer who became the first African-American Supreme Court Justice of the United States despite being denied enrollment to the University of Maryland Law School was Justice Thurgood Marshall.
\end{hwkProblem}

\begin{hwkProblem}{8}{}*
	What is the name of the Maryland land-grant institution, established after the second Morrill Act, to provide access to education for people of color?

	\hwkSol

	The name of the Maryland land-grant institution to provide access to education for people of color is the University of Maryland, Eastern Shore.
\end{hwkProblem}

\begin{hwkProblem}{9}{}*
	What is the name of the Marylander that challenged Thomas Jefferson’s views of racial inferiority through written correspondence?

	\hwkSol

	The Marylander that challenged Thomas Jefferson's views of racial inferiority through written correspondence was Benjamin Banneker.
\end{hwkProblem}

\begin{hwkProblem}{10}{}*
	What was the name of the first Black undergraduate student at the University of Maryland?

	\hwkSol

	The first Black undergraduate student at the University of Maryland was Hiram Whittle.
\end{hwkProblem}

\end{document}
