\input{/Users/vsrivastava/files/uni/msc/tex/HWSetup}

%
% Homework Details
%   - Title
%   - Due date
%   - Due time
%   - Course
%   - Section/Time
%   - Instructor
%   - Author
%

\newcommand{\hmwkTitle}{Final Project Documentation}
\newcommand{\hmwkDueDate}{December 16, 2024}
\newcommand{\hmwkDueTime}{11:59 PM}
\newcommand{\hmwkClass}{ENAE 380}
\newcommand{\hmwkClassTime}{0106}
\newcommand{\hmwkClassInstructor}{Dr. Mumu Xu}
\newcommand{\hmwkAuthorName}{\textbf{Vai Srivastava}}
\newcommand{\hmwkCompletionDate}{\today}

\begin{document}

\maketitle

\pagebreak

\section{Prerequesites}
It is necessary to have the following:
\begin{itemize}
    \item \lstinline{rust}
    \item \lstinline{libtorch}
\end{itemize}

These can be installed manually from \href{https://rustup.rs}{rustup} and \href{https://pytorch.org/get-started/locally/}{pytorch}. As well, you must set the \lstinline{libtorch} path.

These steps can be achieved on macOS (using Homebrew) through the \lstinline{./requirements-macos.sh} script. The script assumes your user shell is POSIX compliant (as is \lstinline{bash}, the default on macOS). I have included a \lstinline{./requirements-macos.fish} script for users who use the \lstinline{fish} shell.

If you require a manual method (i.e. in the case you are not on macOS or do not have Homebrew), the following should suffice (filling in your machine's information where needed):

\begin{lstlisting}[language=bash]
<your-package-manager> install rust pytorch
export LIBTORCH=/your/path/to/pytorch
export LD_LIBRARY_PATH=${LIBTORCH}/lib:$LD_LIBRARY_PATH
\end{lstlisting}

Likewise in fish:

\begin{lstlisting}[language=bash]
<your-package-manager> install rust pytorch
set -x LIBTORCH /your/path/to/pytorch
set -x LD_LIBRARY_PATH $LIBTORCH/lib $LD_LIBRARY_PATH
\end{lstlisting}

\section{Installation and Running}
Now we simply need to download the repository and we can run the program!

\begin{lstlisting}[language=bash]
git clone "github.com/vaisriv/nfl-rss-nlp" ./nfl-rss-nlp
cd ./nfl-rss-nlp
cargo run --release
\end{lstlisting}

Of note, on first run, you will likely need to download the \lstinline{rust-bert} Question-Answering model. This can be quite large, and may take a while. Be patient! Your Super Bowl answers are near!

Details on how to run the program and its features are available within the manpage (accessed via \lstinline{man ./nfl-rss-nlp.1}), or through the cli help menu (accessed via \lstinline{cargo run --release -- --help}).

As \lstinline{pytorch} is not compiled into the program, \lstinline{nfl-rss-nlp} must be run through \lstinline{cargo}. As such, necessary command line arguments can be passed through the following syntax:
\begin{lstlisting}[language=bash]
cargo run --release -- [OPTIONS]
\end{lstlisting}

\section{Acknowledgements}
This project would not be possible without the following:
\begin{itemize}
    \item \href{https://crates.io/crates/rust_bert}{rust-bert}
    \item \href{https://pytorch.org/}{pytorch}
    \item \href{https://huggingface.co/}{huggingface}
\end{itemize}

\end{document}
